### 2014-10-20 PrivacyProtection-2014-09-09.tex
local changes

Defining privacy is a challenge which seems impossible. This is well put to words by Serge Gutwirth, who notes:

\begin{quote}
The notion of privacy remains out of the grasp of every academic chasing it. Even when it is cornered by such additional modifiers as `our' privacy, it still finds a way to remain elusive. \cite{Gutwirth}
\end{quote}

%Many researchers seem to only ``focus on the ways in which privacy can be infringed'' \cite{7ToP}.
%Thus they try to create taxonomies of \emph{privacy harms} instead of taxonomies of \emph{privacy types}.
%Those two differ in the respect that the former focuses on threats to prohibit whereas the latter focuses on values to protect.
%So one should rather evaluate what aspects are precious about privacy and develop measures to ensure their security than only forbid single actions against it \cite{7ToP}.

Many researchers seem to only ``focus on the ways in which privacy can be infringed'' \cite{7ToP}.
Thus they invest a great amount of work in defining threats to prohibit instead of describing why privacy is so valuable to us.
This way around one could derive measures to ensure and secure its value \cite{7ToP}.
One particular scholar who does this in the context of digital monitoring is Charles Fried.
He questioned, why we are so sensitive to violations of privacy.
But he did not assert privacy as an intrinsic value by itself, he rather sated:

\begin{quote}
Privacy is not simply an absence of information about us in the minds of others;
rather it is \textbf{the control we have over information about ourselves}. \cite{CFried:Privacy}
\end{quote}

According to Fried privacy is a \textit{rational context}.
Which means that one is aware of such context's existence during a rational action.
If we are to share private information with others, we are most likely aware that this action is privacy related.
In that case we are able to selectively disclose information along the two dimensions of quantity and quality.
This leads Fried to his thesis, that privacy is one's ability to create and modulate his or hers social relationships, namely: friendship, love and trust. \cite{CFried:Privacy}

Depending on the conversation partner, we change the degree of intimate information we share if it is a total stranger, colleague, close friend or lover.
With close friends or lovers we share information of great intimacy we do not share with anyone else.
Moreover, we trust those friends or lovers to not reveal information about us to others by respecting their privacy.
Trust needs the possibility of unknown failure.
If we would constantly monitor our partners, they cannot fail unnoticed nor can they willingly share that information with us.
Thus they could not trust us anymore. \cite{CFried:Privacy}

So privacy or the its possibility, according to Fried, is the foundation of our core relations: friendship, love and trust.
And thus it is valuable, because those relations are essential to human society \cite{CFried:Privacy}. 
Using his anatomy of privacy as foundation of our analysis is suitable because of two points.
At first, Fried's study on the understanding of privacy provided a great contribution to the research on the same term in philosophy \cite{sep-privacy} and computer science \cite{SociotechnicalArchitectureForOnlinePrivacy}.
Secondly, despite the fact his text was published in 1970, he already included technologies to its viewpoint that did not only monitor location, but also record biometric data.

@@

\textbf{System Complexity vs Privacy:}
System Providers offer a service to Local Authorities, which is to provide and maintain a monitoring and mining system, e.g. for public mobility.
This system shall produce business intelligence, so that Local Authorities can improve their public services.
This task in it self has a high technical complexity and is the sole asset with financial return for System Providers.
However, this task operates on privacy sensitive data provided by monitored Citizens.
In order to ensure their privacy, System Provider would have to implement additional mechanisms, which allow Citizens to exercise control of their data.
This will not only raise the complexity of the monitoring and mining system, System Providers also have to layout the complexity in a comprehensible manner.
To effectively enable Citizens to preserve their privacy, they need to know what happens with their data.

@@

\subsubsection{Vulnerabilities}
\label{subsubsection:Vulnerabilities}
This section outlines the vulnerabilities (Figure \ref{figure:Live+Gov Vulnerabilities}) of the proposed monitoring and mining system.
Note that vulnerabilities are not necessarily of technical nature.
The weaknesses of IT systems are often created due to misuse or misconfiguration of the various components by one or more actors.

@@

\subsubsection{Threats}
This section outlines the potential threats (Figure \ref{figure:Live+Gov Threats}) for Citizen privacy in the proposed monitoring and mining System.
We derive threats from known conflicts of interests \ref{subsubsection:Conflicts of Interests} and vulnerabilities \ref{subsubsection:Vulnerabilities}
=======
\subsection{Step 2. Potential Analysis}

@@

\paragraph{The 7 C's of user privacy control (Figure \ref{figure:The Seven Cs of User Privacy Control})}

@@

\subparagraph{Comprehension}

@@

\subparagraph{Consciousness \textbf{(critical!)}}

@@

\subparagraph{Choice}

@@

\subparagraph{Consent}

@@

\subparagraph{Context}

@@

\subparagraph{Confinement}

@@

\subparagraph{Consistency}

@@

\paragraph{The 2 Steps of the 7 C's (Figure \ref{figure:The 2 Steps of the 7 Cs of User Privacy Control})}

@@

\subparagraph{(I) Enable \emph{Adequate} Control}

@@

\subparagraph{(II) Enable \emph{Actual} Control}

@@

% \section{References}

>>>>

Defining privacy is a challenge which seems impossible. This is well put to words by Serge Gutwirth, who notes in \cite{Gutwirth}:

\begin{quote}
The notion of privacy remains out of the grasp of every academic chasing it. Even when it is cornered by such additional modifiers as `our' privacy, it still finds a way to remain elusive.
\end{quote}

Many privacy researchers seem to ``focus on the ways in which privacy can be infringed'' \cite{1}.
Thus they try to create taxonomies of \emph{privacy harms} instead of taxonomies of \emph{privacy types}.
Those two differ in the respect that the former focuses on threats to prohibit whereas the latter focuses on values to protect.
So one should rather evaluate what aspects are precious about privacy and develop measures to ensure their security than only forbid single actions against privacy \cite{1}.

@@

\textbf{System Complexity vs Privacy:}
System Providers offer a service to Local Authorities, which is to provide and maintain a monitoring and mining system, e.g. for public mobility.
This system shall produce business intelligence, so that Local Authorities can improve their public services.
This task in it self has a high technical complexity and is the sole asset with financial return for System Providers.
However, this task operates on privacy sensitive data provided by monitored Citizens.
In order to ensure their privacy, System Provider would have to implement additional mechanisms, which allow Citizens to exercise control of their data.
But this will eventually raise the complexity of the monitoring and mining system.

@@

\subsubsection{Vulnerabilities}
This section outlines the vulnerabilities (Figure \ref{figure:Live+Gov Vulnerabilities}) of the proposed monitoring and mining system.
Note that vulnerabilities are not necessarily of technical nature.
The weaknesses of IT systems are often created due to misuse or misconfiguration of the various components by one or more actors.

@@

@@

\textbf{The 7 C's of user privacy control (Figure \ref{figure:The Seven Cs of User Privacy Control})}

@@

\item
\textbf{Comprehension}

@@

\item
\textbf{Consciousness \textbf{(critical!)}}

@@

\item
\textbf{Choice}

@@

\item
\textbf{Consent}

@@

\item
\textbf{Context}

@@

\item
\textbf{Confinement}

@@

\item
\textbf{Consistency}

@@

\textbf{The 2 Steps of the 7 C's (Figure \ref{figure:The 2 Steps of the 7 Cs of User Privacy Control})}

@@

\item
\textbf{Enable \emph{Adequate} Control}

@@

\item
\textbf{Enable \emph{Actual} Control}

@@

\end{enumerate}
